Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2015-02-06 paper_linheng_7.tex
update proof

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Energy conservation has become a major challenge to the Internet. In existing approaches, a part of line cards
are switched into sleep mode for energy conservation, and the routing is configured carefully to balance energy saving
and traffic engineering goals, such as the maximum link utilization ratio (MLUR). Typically, traffic demands are
used as inputs, and routing is computed accordingly. However, accurate traffic matrices are difficult to obtain and
are changing frequently. This makes the approaches difficult to implement. Further, the routing may shift
frequently, and is not robust to sudden traffic changes.

In this paper, we propose a different approach that finds one energy-aware routing robust to a set of traffic
matrices, particularly to arbitrary traffic demands. Such a routing without energy consideration is known as
the demand-oblivious routing, and is well studied. However, the problem becomes much more challenging when energy
conservation is involved. To overcome the challenges, we first define a new metric, namely oblivious performance
ratio with energy constraint (OPRE), which reflects the MLUR distance from a routing to the optimal routing when
certain energy conservation requirement is satisfied. We model the problem of minimizing the performance ratio,
and analyze the lower and the upper bounds. Then, we propose Robust Energy-Aware Routing (REAR) to solve
the problem in two phases. REAR select sleeping links based on extended robust link utilization (ERLU)
and compute the routing based on a classical demand-oblivious routing algorithm.
We evaluate our algorithms on real and synthetic topologies. The simulation results show that REAR can save
19\% of line card power while the performance ratio is less than 34\%.
\end{abstract}

@@

In this paper, we overcome the aforementioned challenges. First, we define a new metric, namely the oblivious performance ratio with energy constraint (OPRE). The OPRE reflects the MLUR distance from a routing to the optimal one when certain energy conservation requirement is satisfied. We model the problem of minimizing the OPRE. Second, we prove that there exists a robust energy efficient routing with the minimum OPRE, which has an upper bound given a network. Then, we propose Robust Energy-Aware Routing (REAR) scheme, which uses heuristic algorithms to solve the problem. We develop algorithm RLP, which chooses sleeping line cards in a way that the OPRE can be minimized potentially. We then develop algorithm RRA to compute the routing in the remaining topology, by extending existing optimal demand-oblivious routing algorithm. We evaluate our algorithms by simulations on real topologies and synthetic traffic demands with random fluctuations. The results show that REAR can achieve an OPRE of 1.34 while 19\% of line card power is saved.

@@

\section{Related Work}
\label{related_work}
Green routing is studied because we can not use as much of a resource as we need \cite{networking:designing}, such as line cards always work in full mode even with 
low traffic fraction. So there are many studies to save energy consumption by put some links in sleep mode, for example GreenTE \cite{networking:greente} is 
proposed for maximuming the sleeping links while $E^2$-MCRA \cite{networking:active} is proposed for minimizing the active links and nodes by a depth-first search approach.
Besides these centralized algorithms, EAR \cite{networking:car} and GRiDA \cite{networking:grida} are proposed for distributed deployment, both of them are compatible 
with OSPF sharing additional information between nodes. For addressing the problem of routing convergence when traffic changes frequently, GreenFRR 
\cite{networking:greenfrr} is proposed by leveraging the technique of fast rerouting.

Network may suffer from bad performance because of both frequent traffic demand and routing changes. There are studies to estimate traffic matrices in the context
of Internet traffic, such as LP approach \cite{networking:lp}, Bayesian Infereence techniques \cite{networking:bayesian} and Time-Varying Network Tomography
\cite{networking:time}. All the estimatation for traffic matrices result in the changes of routing, \cite{networking:minimize} proposed an oblivious routing algorithm with a polylog 
competitive ratio with respect to congestion and \cite{networking:polynomial} give a polynomial time algorithm based on applying the Ellipsoid algorithm to an exponential-size LP model.
To be practical for large networks, the oblivious-demand routing based on polynomial-size LP formulation is investigated in \cite{networking:oblivious}.

In this paper, we proposed robust energy-aware routing based on the oblivious-demand \cite{networking:oblivious}, which is both green for the energy consumption by pruning
some links based on ERLU, and also robust for uncertain traffic demands. It is more practical than existing green routing algorihtm because it almost do not need changes when 
real traffic varifies.

@@

The intrinsic reason for such a ``fake robust'' is that the topology is not changing when performance ratio is computed in Eq. (\ref{equation_P_rmG}). To address this issue, we extend the definition of OPR. Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Eq. (\ref{inequation_power_threshold})). Note that in this case, a path cannot traverse a sleeping link, so routing $r$ is limited by $G^*$ (Eq. (\ref{equation_flow_for_routing}) in Section III.C). The extended performance ratio is defined as
\begin{equation}
\label{equation_P_rmGG}
	P(r, \{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
\end{equation}
Let $P^*(r, M, G, G^*)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$. We define $P^*(r, M, G, G^*)$ by extending $m$ to $M$. Similar to Eq. (\ref{equation_P_rMG}), we have
\begin{equation}
\label{equation_P_rMGG}
	P^*(r, M, G, G^*) = \max_{m\in M} P(r, \{ m \}, G, G^*).
\end{equation}
Note that $G^*$ is used to achieve certain energy conservation target. For an energy conservation target, there may exist a set of different $G^*$, which result in different OPRE. We will show an example below. When there is no energy constraint, $G^*$ equals $G$, and Eq. (\ref{equation_P_rMGG}) naturally reduces to Eq. (\ref{equation_P_rMG}).

@@

Constraints (\ref{equation_U_rmG}), (\ref{equation_P_rmGG}), and (\ref{equation_P_rMGG}) follow our definition of the OPRE. Eq. (\ref{equation_flow_for_routing_second}) means that the optimal routing $r'$ in $G$ must be a valid routing, i.e. with routing consistency. Specifically, for the source/destination node, all traffic must be routed/received; and for an intermediate node, the traffic flowing out must equal the traffic flowing in. Similarly, Eq. (\ref{equation_flow_for_routing}) means that the robust routing $r$ in $G^*$ must be a valid routing. Ineq. (\ref{inequation_traffic_fraction}) means that the range of $f^r_{ab}(i,j)$ and $f^{r'}_{ab}(i,j)$ is from 0 to 1. Ineq. (\ref{inequation_power_threshold}) means that the power consumption of links in $G^*$ must be less than a given threshold. In Ineq. (\ref{inequation_power_threshold}), $\theta$ denotes the power saving ratio we must achieve by using $G^*$. Here, we use $p(l)$ to denote the power consumption of link $l$, which is mainly drawn by the line cards at the two ends of the link. Note that $p(l)$ is independent of the traffic volume, and this assumption is based on the fact that in current stage, the power of a line card changes little with the traffic volume \cite{networking:hopbyhop}.

@@

Theorem 3 tells us that the minimum OPRE is related to the link capacity difference in the network. The above results are for $\theta = 0$. Now let us see the results for a large $\theta$. Since there is not much difference between the power consumptions for links with different capacities \cite{networking:hopbyhop}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$. We have
\begin{theorem}
Let $G^*$ be a spanning tree of a cycle on $n$ nodes, and then the upper bound of the OPRE is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$.
\end{theorem}
\begin{proof}
See Appendix B.
\end{proof}
\begin{theorem}
Let $G^*$ be a spanning tree of a complete graph on $n$ nodes, and then the upper bound of the OPRE is $\frac{n^2}{2} \frac{\max cap_{ij}}{\min cap_{ij}}$.
\end{theorem}
\begin{proof}
See Appendix C.
\end{proof}

@@

Several heuristics have been proposed to select sleeping links without the knowledge of a specific TM, with various considerations \cite{}\cite{}\cite{}. However, we need a algorithm that can potentially minimize the OPRE. To this end, we first find the demand-oblivious routing that minimizes the OPR, using the linear programming approach in \cite{networking:oblivious}. Bases on the routing, we define the extended robust link utilization (ERLU), to evaluate the contribution of a link to the OPRE.

@@

Note that there may be multiple paths in $r_0$ between a source-destination pair. We first decompose the paths by a standard procedure given in \cite{}. Formally, let $p^h_{ab}$ denote the $h$-th path between nodes $a$ and $b$, and $t^h_{ab}$ be the fraction of the traffic that is routed on $p^h_{ab}$. For each $p^h_{ab}$ that traverses a sleeping link, we must find some detour paths to absorb $t^h_{ab}$. Such detour paths should not increase the OPRE too much. Recall that ERLU $u^e_{ij}(r)$ reflects the link utilization ratio without the knowledge of the TM, under routing $r$. Thus, we prefer a path whose maximum $u^e_{ij}(r)$ is small. On the other hand, the detour paths should not be too long, in order to limit the path stretch. To this end, we use YEN's algorithm \cite{networking:yens} to compute the $k$-th shortest path in graph $G^*$. We develop Algorithm RRA.

@@

The inputs of RRA include graph $G(V,E)$, sleeping link set $S$, optimal demand-oblivious routing $r_0$ in $G$, and $N$ which will be used latter. The output is the robust energy efficient routing $r$. $G^*$ and $r$ are initialized in Step 1. The main loop from Step 2 to Step 14 finds the detour paths for each sleeping link in $S$, and for each source-destination pair. The traffic fraction that should be detoured is denoted by $t$ (Step 4), and the original paths are extracted and removed from routing $r$ (Steps 5 to 8). Then, the $k$-th shortest paths are computed in Step 9. The traffic fraction of $t$ is detoured by $N$ times evenly (Steps 10 to 14), and the detour path with the minimum value of the ERLU is selected (Steps 11 and 12). In Step 15, the duplicate paths are merges and new routing $r$ that does not traverse link $l$ is obtained. The computation complexity of the RRA algorithm is 
$O((|E|-|V|)|V|^2(|R||E| + K|V|(|E| + |V|\log|V|) + N(|E||V|^2 + K|E|) + |R||E|))$ in the worst case, where $O(|E|-|V|)$ is the maximum number of sleeping links, $O(|V|^2)$ is the maximum
number of OD pairs, $O(|R||E|)$ is for computing detoured traffic and remove failed paths where $O(|R|)$ is the number of input routings, $O(K|V|(|E| + |V|\log|V|))$ is for solving the 
yens algorithm where $K$ is the number of shortest paths, $O(N(|E||V|^2 + K|E|))$ is for detouring traffic fraction by $N$ times, and $O(|R||E|)$ is for merging routings.

\begin{figure*}[!t]
\centering
\vspace*{0.1in}
\subfloat{\includegraphics[width=6cm]{opr_with_power_abilene}}
\subfloat{\includegraphics[width=6cm]{opr_with_power_geant}}
\subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
\caption{OPRE versus TMs: (a). Abilene, (b). Geant, (c). Cernet2}
\label{figure_opr_with_power}
\vspace*{0.1in}
\end{figure*}

\begin{figure*}[!t]
\centering
\vspace*{0.1in}
\subfloat{\includegraphics[width=6cm]{exp2_sort_abilene}}
\subfloat{\includegraphics[width=6cm]{exp2_sort_geant}}
\subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
\caption{OPRE versus Power Saving: (a). Abilene with 4 links removed (b). Geant with 6 links removed (c). Cernet2 with 2 links removed}
\label{figure_exp2_sort}
\vspace*{0.1in}
\end{figure*}

@@

We evaluate the REAR approach by simulations on three real-world network topologies, including Abilene \cite{networking:abilene}, Geant \cite{networking:geant}, and CERNET2 \cite{networking:cernet2}. The numbers of nodes and links of the topologies are listed in Table \ref{table_topology}. The traffic matrices we used in our simulations are generated as follows. We first generate a baseline traffic matrix using the gravity model \cite{networking:gravity}, where the baseline traffic demand $d_{ab}$ is proportional to their total capacity. Then, the traffic demand is generated randomly in the range from $d_{ab}/\omega$ to $d_{ab}\omega$, where $\omega \geq 1$ is a margin factor used to control the fluctuation range of the traffic. We generate 1000 random TMs for each topology with each $\omega$. The power consumption of different line cards is set as constant in the simulations, as shown in Table \ref{table_line_card_power_consumption}, following \cite{networking:greente}.

\begin{table}[h]
\label{table_topology}
\renewcommand{\arraystretch}{1}
\caption{Topologies}
\label{three topologies}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\bfseries Topology & \bfseries Nodes & \bfseries Links & \bfseries Links can be Removed \\
\hline
Abilene & 12 & 15 & 4 \\
\hline
Geant & 23 & 37 & 15 \\
\hline
Cernet2 & 20 & 22 & 3 \\
\hline
\end{tabular}
\end{table}

For comparison, we simulate a recent energy efficient routing approach, namely DMP \cite{networking:dmp}, which also does not use the TMs as inputs. DMP always selects the most power-hungry links to switch into off/sleep mode, and can achieve a large power saving ratio, but does not consider routing robustness. We evaluate the OPRE and its distribution, the power saving ratio, and the path stretch of the approaches.

\begin{table}[h]
\label{table_line_card_power_consumption}
\renewcommand{\arraystretch}{1}
\caption{Line Card Power Consumption}
\label{power model}
\centering
\begin{tabular}{|c|c|c|}
\hline
\bfseries Line-Card & \bfseries Speed(Mbps) & \bfseries Power(Watts) \\
\hline
1-Port OC3 & 155.52 & 60 \\
\hline
8-Port OC3 & 1244.16 & 100 \\
\hline
1-Port OC48 & 2488.32 & 140 \\
\hline
1-Port OC192 & 9953.28 & 174 \\
\hline
\end{tabular}
\end{table}

\begin{figure*}[!t]
\centering
\vspace*{0.1in}
\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
\subfloat{\includegraphics[width=6cm]{exp4_path_geant}}
\subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
\caption{Path Stretching: (a). Abilene, (b). Geant, (c). Cernet2}
\label{figure_exp4_path}
\vspace*{0.1in}
\end{figure*}

\subsection{OPRE versus Power Saving}
Fig. \ref{figure_opr_with_power} (a) shows the OPRE as a function of power saving ratio $\theta$, in the Abilene topology. We see that the OPRE increases when more power is saved.
This is not surprising because the routing becomes less robust when more links are switched into off/sleep mode. Our REAR has an OPRE ranging from 
1.06 to 2.32, which is much less than the results of DMP. This is because REAR takes routing robustness into consideration when it prunes 
links and computes routing. For instance, when $\omega = 3.5$ and 25\% power is saved, the OPRE of REAR is 2.32, while the OPRE of DMP is 5.09. 
This implies that REAR is more robust against traffic uncertainty. We also see that a larger $\omega$ results in a larger OPRE, because 
the traffic volume fluctuates in a wider range. For instance, when $\omega$ increases from 1.5 to 3.5, the OPRE of REAR increases about 
0.17, while the OPRE of DMP increases about 0.53.

Similar results are showed in Fig. \ref{figure_opr_with_power} (b) and (c), namely in Geant and Cernet2 topology. In Geant, we see that OPRE sacle with a wider range both
in DMP and REAR, it is because Geant is much larger than other topologies, when removing too much links, the network will suffer from more 
serious congestion. In Cernet2, Although REAR is better than DMP, the difference is marginal when achieved a large $\theta$. It can be explained
by the density of links, REAR obtains a better performance in dense topology because it will have more choices.

\subsection{OPRE versus Margin}
Fig. \ref{figure_exp2_sort} (a) shows the amount of TMs as a cumulative distribution function (CDF) of OPRE, when remove 4 links in Abilene topology. We see that the curves of
DMP are right of REAR, means REAR always have lower OPRE whatever TMs is. It is consistent with Fig. \ref{figure_opr_with_power} (a). We also observe that our REAR has
more concentrated curves, means REAR have the almost same performance when TM changes, it is because REAR remove the less `important' link from 
topology and the left topology is more robust for TMs than DMP. For instance, REAR ranges from 1.74 to 2.32 while DMP range from 2.97 to 5.09 
when $\omega = 3.5$. Also we can see that curve become smooth when $\omega$ increases, it is because the TMs range from wider scope, and the OPRE
may achieved wider scope too. However we see that whatever $\omega$ is, the center of the curve are almost the same postion. It is because 
we only change the margin $\omega$ rather than the base TM, so the medial value will not changes apparently.

Fig. \ref{figure_exp2_sort} (b) shows the amount of TMs as a CDF of OPRE when remove 6 links in Geant, and Fig. \ref{figure_exp2_sort} (c) shows the situation when remove 2 links in Cernet2.
Similar results are showed in them, however both the centers of REAR curve in Fig. \ref{figure_exp2_sort} (b) and DMP in Fig. \ref{figure_exp2_sort} (c) are not at the same postion 
when $\omega$ changes. The reasons are two-folds, firstly the curves is drawn by sampling from origin data so the center of curve may not the real 
center. On the other hand, we calculate the distance of centers over the scope of OPRE, respectively 0.9\% for REAR in Geant and 0.1\% for DMP in Cernet2,
so it is obvious that from sight of the scope of OPRE, the center of curves are the same `postion'.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Energy conservation has become a major challenge to the Internet. Switching part of components into sleep mode is an effective way for energy conservation. Many existing approaches compute routing based on traffic matrices, to balance energy saving and traffic engineering goals, e.g., the maximum link utilization ratio (MLUR). However, accurate traffic matrices are difficult to obtain and change frequently, resulting in lack of routing stability and robustness.

We propose to find one energy-aware routing robust to a set of traffic matrices. Such demand-oblivious routing problem has been studied without energy conservation, but it becomes more challenging when energy is considered. To overcome the challenges, we define a metric that reflects the MLUR distance from a routing to the optimal routing under certain energy conservation requirement. We model the problem of minimizing the metric, and analyze the upper bounds. Then, we propose a robust energy-aware routing scheme to solve the problem by selecting sleeping links and computing the routing, based on a classical demand-oblivious routing algorithm. We evaluate our algorithms by simulations on real topologies. The results show that REAR is much more robust than existing approaches while more than 35\% line card power can be saved.
\end{abstract}

@@

In this paper, we overcome the aforementioned challenges. First, we define a new metric, namely the oblivious performance ratio with energy constraint (OPRE). The OPRE reflects the MLUR distance from a routing to the optimal one when certain energy conservation requirement is satisfied. We model the problem of minimizing the OPRE. Second, we prove that there exists a robust energy efficient routing with the minimum OPRE, which has an upper bound given a network. Then, we propose Robust Energy-Aware Routing (REAR) scheme, which uses heuristic algorithms to solve the problem. We develop algorithm RLP, which chooses sleeping line cards in a way that the OPRE can be minimized potentially. We then develop algorithm RRA to compute the routing in the remaining topology, by extending existing optimal demand-oblivious routing algorithm. We evaluate our algorithms by simulations on real topologies and synthetic traffic demands with random fluctuations. The results show that REAR can achieve an OPRE of 2.32 while 25\% of line card power is saved.

@@

\section{Related Work}
\label{related_work}
There have been a number of studies on energy conservation in the Internet using energy efficient routing. Many approaches take link utilization as a key factor to avoid network congestions. GreenTE \cite{networking:greente} is proposed to find a routing that can maximize the power saving by off/sleeping components, while the link utilization must be less than a given threshold. $E^2$-MCRA \cite{networking:active} is proposed to find routing for new incoming flows, such that the number of active links and nodes are minimized while the unpredictable traffic increment is considered. ROD \cite{ROD2012Networking} computes the link weights using a Lagrange multiplier method, so as to balance the number of sleeping links and the link utilization under an OSPF-like routing. These approaches have to obtain the traffic matrix/demands in real-time. REsPoNse \cite{Response11Conext} uses MPLS tunnels to aggregate traffic and saves energy by switching under-utilized links into sleep mode; the sleeping links are activated when some link has an utilization ratio larger than a given threshold. This method of activating sleeping links is used in some other approaches \cite{networking:car}\cite{networking:dmp}\cite{networking:grida}\cite{networking:greenfrr}\cite{SPEED14TON}. Although these approaches do not need a traffic matrix, they still need the traffic volume on each link in the network, and the routing may shift frequently with the traffic change. Our study in this paper is different from the above approaches, because we assume the traffic can be uncertain, and we try to find a static routing that minimizes the distance to the optimal routing with respect to link utilization.

Great efforts have been made to optimize the network performance of delivering traffic. Generally, there are two types of approaches for such traffic engineering targets. The first type assumes the awareness of the traffic matrix/demands, while the other deals with uncertain traffic demands \cite{DynamicVSOblivious11Algorithmica}. In this paper, we are interested in the second category, which is called the oblivious routing. R\"{a}cke \cite{networking:minimize} proposes an oblivious routing algorithm with a polylog competitive ratio with respect to congestion. Azar et al. \cite{networking:polynomial} propose a polynomial time algorithm to solve the oblivious routing based on the ellipsoid method. Applegate \cite{networking:oblivious} et al. further simplify the problem into a polynomial-size linear programming model. Li et al. \cite{ASimpleMethodBalancing05ICCCN} propose a penalty method to improve the quality of oblivious routing with respect to path dispersion and path variation. Kodialam et al. \cite{TrafficOblivious07CommuMagazine} study the problem of providing bandwidth guarantee in VPN using oblivious routing. They further extend the application to a set of networking scenarios \cite{ObliviousHighVariable08TON}, and to provide resiliency against link failures \cite{ObliviousHoseModel11TON}. Our work in this paper applies oblivious routing in the scenario of energy conservation. We need a new metric that is suitable for our scenario, and new routing algorithms as well.

@@

The intrinsic reason for such a ``fake robust'' is that the topology is not changing when performance ratio is computed in Eq. (\ref{equation_P_rmG}). To address this issue, we extend the definition of OPR. Formally, let $G^*$ be a sub-graph of $G$ that satisfies the energy constraint (We will formally define the energy constraint in Section III.C, i.e., Ineq. (\ref{inequation_power_threshold})). Note that in this case, a path cannot traverse a sleeping link, so routing $r$ is limited by $G^*$ (Eq. (\ref{equation_flow_for_routing}) in Section III.C). The extended performance ratio is defined as
\begin{equation}
\label{equation_P_rmGG}
	P(r, \{ m \}, G, G^*) = \frac{U_{r,m,G^*}}{\min_{r'} U_{r', m, G}}.
\end{equation}
Let $P^*(r, M, G, G^*)$ be the \emph{oblivious performance ratio with energy constraint} (OPRE) for routing $r$. We define $P^*(r, M, G, G^*)$ by extending $m$ to $M$. Similar to Eq. (\ref{equation_P_rMG}), we have
\begin{equation}
\label{equation_P_rMGG}
	P^*(r, M, G, G^*) = \max_{m\in M} P(r, \{ m \}, G, G^*).
\end{equation}
Note that $G^*$ is used to achieve certain energy conservation target. For an energy conservation target, there may exist a set of different $G^*$, which result in different OPRE. We will show an example below. When there is no energy constraint, $G^*$ equals $G$, and Eq. (\ref{equation_P_rMGG}) naturally reduces to Eq. (\ref{equation_P_rMG}).

@@

Constraints (\ref{equation_U_rmG}), (\ref{equation_P_rmGG}), and (\ref{equation_P_rMGG}) follow our definition of the OPRE. Eq. (\ref{equation_flow_for_routing_second}) means that the optimal routing $r'$ in $G$ must be a valid routing, i.e. with routing consistency. Specifically, for the source/destination node, all traffic must be routed/received; and for an intermediate node, the traffic flowing out must equal the traffic flowing in. Similarly, Eq. (\ref{equation_flow_for_routing}) means that the robust routing $r$ in $G^*$ must be a valid routing. Ineq. (\ref{inequation_traffic_fraction}) means that the range of $f^r_{ab}(i,j)$ and $f^{r'}_{ab}(i,j)$ is from 0 to 1. Ineq. (\ref{inequation_power_threshold}) means that the power consumption of links in $G^*$ must be less than a given threshold. In Ineq. (\ref{inequation_power_threshold}), $\theta$ denotes the power saving ratio we must achieve by using $G^*$. Here, we use $p(l)$ to denote the power consumption of link $l$, which is mainly drawn by the line cards at the two ends of the link. Note that $p(l)$ is independent of the traffic volume, and this assumption is based on the fact that in current stage, the power of a line card changes little with the traffic volume \cite{PowerAware08Infocom}.

@@

Theorem 3 tells us that the minimum OPRE is related to the link capacity difference in the network. The above results are for $\theta = 0$. Now let us see the results for a large $\theta$. Since there is not much difference between the power consumptions for links with different capacities \cite{networking:greenfrr}, we consider the spanning trees of a graph, which can achieve a near-optimal $\theta$. We have
\begin{theorem}
Let $G^*$ be a spanning tree of a cycle on $n$ nodes, and then the upper bound of the OPRE is $1 + \frac{\max cap_{ij}}{\min cap_{ij}}$.
\end{theorem}
\begin{proof}
See Appendix B.
\end{proof}
\begin{theorem}
Let $G^*$ be a spanning tree of a complete graph on $n$ nodes, and then the upper bound of the OPRE is $\frac{n^2}{2} \frac{\max cap_{ij}}{\min cap_{ij}}$.
\end{theorem}
\begin{proof}
See Appendix C.
\end{proof}

@@

Several heuristics have been proposed to select sleeping links without the knowledge of a specific TM, with various considerations \cite{networking:car}\cite{networking:dmp}\cite{networking:grida}\cite{ESACON11InfocomWs}. However, we need a algorithm that can potentially minimize the OPRE. To this end, we first find the demand-oblivious routing that minimizes the OPR, using the linear programming approach in \cite{networking:oblivious}. Bases on the routing, we define the extended robust link utilization (ERLU), to evaluate the contribution of a link to the OPRE.

@@

Note that there may be multiple paths in $r_0$ between a source-destination pair. We first decompose the paths by a standard procedure given in \cite{networkflow93book}. Formally, let $p^h_{ab}$ denote the $h$-th path between nodes $a$ and $b$, and $t^h_{ab}$ be the fraction of the traffic that is routed on $p^h_{ab}$. For each $p^h_{ab}$ that traverses a sleeping link, we must find some detour paths to absorb $t^h_{ab}$. Such detour paths should not increase the OPRE too much. Recall that ERLU $u^e_{ij}(r)$ reflects the link utilization ratio without the knowledge of the TM, under routing $r$. Thus, we prefer a path whose maximum $u^e_{ij}(r)$ is small. On the other hand, the detour paths should not be too long, in order to limit the path stretch. To this end, we use YEN's algorithm \cite{networking:yens} to compute the $k$-th shortest path in graph $G^*$. We develop Algorithm RRA.

@@

The inputs of RRA include graph $G(V,E)$, sleeping link set $S$, optimal demand-oblivious routing $r_0$ in $G$, and $N$ which will be used latter. The output is the robust energy efficient routing $r$. $G^*$ and $r$ are initialized in Step 1. The main loop from Step 2 to Step 14 finds the detour paths for each sleeping link in $S$, and for each source-destination pair. The traffic fraction that should be detoured is denoted by $t$ (Step 4), and the original paths are extracted and removed from routing $r$ (Steps 5 to 8). Then, the $k$-th shortest paths are computed in Step 9. The traffic fraction of $t$ is detoured by $N$ times evenly (Steps 10 to 14), and the detour path with the minimum value of the ERLU is selected (Steps 11 and 12). In Step 15, the duplicate paths are merges and new routing $r$ that does not traverse link $l$ is obtained. The computation complexity of the RRA algorithm is polynomial. We omit the detail due to the space limitation.
\ignore{
$O((|E|-|V|)|V|^2(|R||E| + K|V|(|E| + |V|\log|V|) + N(|E||V|^2 + K|E|) + |R||E|))$ in the worst case, where $O(|E|-|V|)$ is the maximum number of sleeping links, $O(|V|^2)$ is the maximum
number of OD pairs, $O(|R||E|)$ is for computing detoured traffic and remove failed paths where $O(|R|)$ is the number of input routings, $O(K|V|(|E| + |V|\log|V|))$ is for solving the
yens algorithm where $K$ is the number of shortest paths, $O(N(|E||V|^2 + K|E|))$ is for detouring traffic fraction by $N$ times, and $O(|R||E|)$ is for merging routings.}

\begin{figure*}[!t]
\centering
\subfloat{\includegraphics[width=6cm]{opr_with_power_abilene}}
\subfloat{\includegraphics[width=6cm]{opr_with_power_geant}}
\subfloat{\includegraphics[width=6cm]{opr_with_power_cernet2}}
\vspace{-0.1in}
\caption{OPRE in (a) Abilene. (b) Geant. (c) CERNET2.}
\label{figure_opr_with_power}
\vspace{-0.1in}
\end{figure*}

\begin{figure*}[!t]
\centering
\subfloat{\includegraphics[width=6cm]{exp2_sort_abilene}}
\subfloat{\includegraphics[width=6cm]{exp2_sort_geant}}
\subfloat{\includegraphics[width=6cm]{exp2_sort_cernet2}}
\vspace{-0.1in}
\caption{Performance ratio in (a) Abilene with 4 links pruned. (b) Geant with 6 links pruned. (c) CERNET2 with 2 links pruned.}
\label{figure_exp2_sort}
\vspace{-0.1in}
\end{figure*}

@@

We evaluate the REAR approach by simulations on three real-world network topologies, including Abilene \cite{networking:abilene}, Geant \cite{networking:geant}, and CERNET2 \cite{networking:cernet2}. The numbers of nodes and links of the topologies are listed in Table \ref{three_topologies}. The traffic matrices we used in our simulations are generated as follows. We first generate a baseline traffic matrix using the gravity model \cite{networking:gravity}, where the baseline traffic demand $d_{ab}$ is proportional to the total capacity of nodes $a$ and $b$. Then, the traffic demand is generated randomly in the range from $d_{ab}/\omega$ to $d_{ab}\omega$, where $\omega \geq 1$ is a margin factor used to control the fluctuation range of the traffic. We generate 1000 random TMs for each topology with each $\omega$. The power consumption of different line cards is set as constant in the simulations, as shown in Table \ref{table_line_card_power_consumption}, following \cite{networking:greente}.

\begin{table}[h]
\renewcommand{\arraystretch}{1}
\caption{Topologies}
\label{three_topologies}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
\bfseries Topology & \bfseries Nodes & \bfseries Links & \bfseries Links can be Removed \\
\hline
Abilene & 12 & 15 & 4 \\
\hline
Geant & 23 & 37 & 15 \\
\hline
CERNET2 & 20 & 22 & 3 \\
\hline
\end{tabular}
\end{table}

For comparison, we simulate a recent energy efficient routing approach, namely DMP \cite{networking:dmp}, which also does not use the TMs as inputs. DMP always selects the most power-hungry links to switch into off/sleep mode, and can achieve a large power saving ratio, but does not consider routing robustness. For the approaches, we evaluate the OPRE, the power saving ratio, the distribution of the performance ratio, and the path stretch.

\begin{table}[h]
\renewcommand{\arraystretch}{1}
\caption{Line Card Power Consumption}
\label{table_line_card_power_consumption}
\centering
\begin{tabular}{|c|c|c|}
\hline
\bfseries Line-Card & \bfseries Speed(Mbps) & \bfseries Power(Watts) \\
\hline
1-Port OC3 & 155.52 & 60 \\
\hline
8-Port OC3 & 1244.16 & 100 \\
\hline
1-Port OC48 & 2488.32 & 140 \\
\hline
1-Port OC192 & 9953.28 & 174 \\
\hline
\end{tabular}
\end{table}

\begin{figure*}[!t]
\centering
\subfloat{\includegraphics[width=6cm]{exp4_path_abilene}}
\subfloat{\includegraphics[width=6cm]{exp4_path_geant}}
\subfloat{\includegraphics[width=6cm]{exp4_path_cernet2}}
\vspace{-0.1in}
\caption{Path Stretch in (a) Abilene. (b) Geant. (c) CERNET2.}
\label{figure_exp4_path}
\vspace{-0.1in}
\end{figure*}

\subsection{OPRE versus Power Saving}
Fig. \ref{figure_opr_with_power} (a) shows the OPRE (evaluated by the maximum performance ratio under all 1000 TMs), as a function of power saving ratio $\theta$, in the Abilene topology. We see that the OPRE increases when more power is saved. This is not surprising because the routing becomes less robust when more links are switched into off/sleep mode. Our REAR has an OPRE ranging from 1.06 to 2.32, which is much less than the results of DMP. This is because REAR takes routing robustness into consideration when it prunes
links and computes routing. For instance, when $\omega = 3.5$ and 25\% power is saved, the OPRE of REAR is 2.32, while the OPRE of DMP is 5.09.
This implies that REAR is more robust against traffic uncertainty. We also see that a larger $\omega$ results in a larger OPRE, because
the traffic volume fluctuates in a wider range. For instance, when $\omega$ increases from 1.5 to 3.5, the OPRE of REAR increases about
0.17, while the OPRE of DMP increases about 0.53.

Fig. \ref{figure_opr_with_power} (b) shows the OPRE as a function of power saving ratio $\theta$ in Geant. We find that the results are similar to that in Abilene. However, the OPRE is larger in Geant than in Abilene for both REAR and DMP. One reason for this result is that Geant has a larger link density ($\frac{37}{23} = 1.61$) than Abilene ($\frac{15}{12} = 1.25$). Another reason is that the link capacity difference is large in Geant. The maximum link capacity is 9920 Mbps while the minimum link capacity is 155 Mbps. Such results are consistent with our analysis in Section IV.

Fig. \ref{figure_opr_with_power} (c) shows the results in CERNET2. We observe that the difference between REAR and DMP is small. This is because the CERNET2 topology has a small link density, and only a small number of links can be pruned.

\subsection{Performance Ratio Distribution}
Fig. \ref{figure_exp2_sort} (a) shows the CDF of random TMs as a function of the performance ratio, in Abilene with 4 links pruned. The curves of REAR are on the left of DMP, which means that REAR has a lower performance ratio under all TMs. We observe that the performance ratio has a larger range with a larger $\omega$, but the performance ratio of REAR has a small range in total (e.g., from 1.74 to 2.32 when $\omega = 3.5$), unlike DMP (e.g., from 2.97 to 5.09 when $\omega = 3.5$). This implies that REAR is more robust.

Fig. \ref{figure_exp2_sort} (b) shows the results in Geant with 6 links pruned, and Fig. \ref{figure_exp2_sort} (c) shows the results in CERNET2 with 2 links pruned. The results are similar to that in Abilene.

\subsection{Path Stretch}

Now we evaluate the path stretch of the approaches, which reflects the end-to-end delay increment due to link pruning and robust routing. Here, path stretch is the ratio of the path length of a routing to the shortest path length, in the topology after pruning links. Note that there may be multiple paths in the robust routing for a source-destination pair. In such a case, we compute the weighted path stretch of these paths according to the traffic fraction they carry.

Fig. \ref{figure_exp4_path} (a) shows the path stretch as a function of pruned link number in Abilene. Generally, the path stretch decreases when more links are pruned, and equals 1 when 4 links are pruned. This is because the topology becomes less connected when more links are pruned, and reduces to a spanning tree when 4 links are pruned. The path stretch of REAR is less than 1.32, because we use YEN's algorithm to find the $k$-th shortest path when searching for paths to detour the traffic. We think this path stretch is small and will not induce large end-to-end delay increment. The path stretch of REAR is a little larger than that of DMP in some cases. This is because most links in Abilene has the same capacity and consumes the same power, and in such a case, DMP randomly selects sleeping links, which may result in less path stretch. We also observe that the path stretch increases with $\omega$, because the demand-oblivious routing is computed based on $\omega$, and when $\omega$ increases, the routing will use more paths to increase the robustness.
